---
title: "Demo of `eur` and `eurusds` Functions"
author: Ilda Kacerja
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Load necessary libraries. 

```{r setup, message=FALSE, warning=FALSE}
library(foRex)
library(binancer)
library(data.table)
library(ggplot2)
```

Use function `binancer::binance_klines` to get the data for bitcoin prices in the last 45 days. 

```{r}
# Getting data
coin_prices <- binance_klines('BTCUSDT', interval = '1d', limit = 45) 
coin_prices[, date := as.Date(close_time)]
coin_prices <- coin_prices[, .(btcusd_price = close, date, volume)]
head(coin_prices)
dim(coin_prices)
# Set key for further merge
setkey(coin_prices, date)
```

The dataset has last 45 days of bitcoin prices in $ and volume.


Use function `foRex::eurusds` to get exchange rates $ to €, for the range of dates we are interested on (in this case the last 45 days). 

```{r}
earliest_date <- min(coin_prices$date)
latest_date <- max(coin_prices$date)
# get exchange rates
exchange_rates <- eurusds(earliest_date, latest_date)
head(exchange_rates)
dim(exchange_rates)
# Set key for further merge
setkey(exchange_rates, date)
```

Exchange rates are not available for weekends and holidays, this explains the dataset with only 29 exchange rates instead of 45. 
The missing values will be imputed with the latest exchange rates available. 

```{r}
coin_prices <- exchange_rates[coin_prices, roll = TRUE]
head(coin_prices)
```

The overall value of the bitcoin (in EUR) is calculated like below.

```{r}
coin_prices <- coin_prices[, value_eur := usdeur*btcusd_price*volume]
head(coin_prices)
```

Below you can see the overall value of bitcoin in EUR for the past 45 days.

Use function `foRex::eur` to format the y-axis values.

```{r, fig.align='center', fig.width=7}
ggplot(coin_prices, aes(date, value_eur)) + geom_line() + 
  theme_bw() + 
  scale_y_continuous(labels = eur) + labs(title = "BTC Overall Value (€)",
                                          subtitle = "Past 45 days",
                                          x = " ", 
                                          y = "")
```
